### 2024-04-28 thesis/chapters/06-conclusion.tex
Complete assets in thesis

\chapter{Conclusion} \label{section:conclusion}  
In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

@@

Feature selection methods should be incorporated into incremental learning. Hyperparameters shall be adjusted, and the balancing method used to increase model performance. The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

>>>>

\chapter{Conclusion} \label{section:conclusion}  
%TODO
In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

@@
